Notes

### 2020-03-24 Notes/Notes.tex

Time dependent Hamiltoniain is
\begin{align}
H_{anneal}(t) =  \frac{-A(t)}{2} (\sum_i \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} J_{ij} \sigma^z_i \sigma^z_j +\sum_i h_i \sigma^z_i ) 
\end{align}

The goal is to solve 
\begin{align}
i \partial_t \psi(t) = H(t) \psi(t)
\end{align}
with initial condition
\begin{align}
\psi(t=0)= \otimes_i  |\rightarrow \rangle_i
\end{align}

@@

For now the offset is included in the following way: 
\begin{align}
H_{offset}(t) =  \frac{-A(t)}{2} ( \sum_i c_i(t) \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} \frac{c_i(t)+c_j(t)}{2} \sigma^z_i \sigma^z_j +\sum_i  c_i(t) \sigma^z_i ) 
\end{align}

So the total Hamiltonian is $H=H_{anneal}+H_{offset}$.

Users can define functions $c_i(t)$, $A(t)$, $B(t)$ in the code.

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{annealingschedule.png}
	\includegraphics[width=0.5\textwidth]{probt.png}
	\caption{
		\label{tdse} time-dependent Schrodinger equation simulation of quantum annealing.
	}
\end{figure}

>>>>

Time dependent Hamiltoniain is
\begin{align}
H_{anneal}(t) =  \frac{-1}{2} (\sum_i  A_i(t)\sigma^x_i) + \frac{1}{2} (\sum_{i>j} \frac{B_{i}(t)+B_{j}(t)}{2} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i ) ,
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site-dependence taking into account of possible annealing offsets.

The goal is to solve 
\begin{align}
i \partial_t \psi(t) = H(t) \psi(t) .
\end{align}

The initial condition is the ground state of $H(s=0)$. This state is slightly different from the pure transverse  field eigenstate $\psi(t=0)= \otimes_i  |\rightarrow \rangle_i$, because the annealing schedule $B_i(s=0)> 0$.

@@

\begin{figure}[htb]
	\centering
	%\includegraphics[width=0.5\textwidth]{annealingschedule.png}
	\includegraphics[width=0.5\textwidth]{probt.png}
	\caption{
		\label{tdse} time-dependent Schrodinger equation simulation of quantum annealing. Annealing time=100 $\mu s$.
	}
\end{figure}
